### 2024-04-21 sections/1-introduction.tex
minor edits

Researchers are collecting data at an unprecedented scale.
In many fields, the sizes of datasets are growing exponentially, and this increase in the rate of data collection outpaces the rate of improvements in computing performance as predicted by Moore's Law~\cite{kahn2011future}.
This indicates that computer architecture will not ``catch up'' to computational needs in the near future.
Often dubbed ``the Big Data explosion,'' this phenomenon has created a need for better algorithms to analyze large datasets.

@@

Given some measure of similarity between data points, e.g. a distance function, there are two common definitions of similarity search: $k$-nearest neighbor search ($k$-NN) and $\rho$-nearest neighbor search ($\rho$-NN).
$k$-NN search aims to find the $k$ most similar points to a query point, while $\rho$-NN search aims to find all points within a similarity threshold $\rho$ of a query point.

>>>>

Researchers are collecting data at an unprecedented scale.
In many fields, the sizes of datasets are growing exponentially, and this increase in the rate of data collection outpaces improvements in computing performance as predicted by Moore's Law~\cite{kahn2011future}.
This indicates that the performance computer hardware will not ``catch up'' to computational needs in the near future.
Often dubbed ``the Big Data explosion,'' this phenomenon has created a need for better algorithms to analyze large datasets.

@@

Given some measure of similarity between data points, e.g. a distance function, there are two common definitions of similarity search: $k$-nearest neighbor search ($k$-NN) and $\rho$-nearest neighbor search ($\rho$-NN).
$k$-NN search aims to find the $k$ most similar points to a query, while $\rho$-NN search aims to find all points within a similarity threshold $\rho$ of a query.
